Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data

### 2023-01-31 analysis/paper_draft3.Rmd
edits to introduction section

Simply pooling the the strike data from current and past trials, and analyzing such data together, ignores such incompatibility, which can lead to inflated type I error and reduced power [@Bennett2020]. To increase power, one may use other methods, such as stratifying strike data by trial and applying the Cochran-Mantel-Haenszel (CMH) test [@Gastwirth2014, 295-297]. Such approaches, however, do not directly address incompatibility between current and historical strike data. For example, applying the CMH test requires first selecting only historical strike data from past trials that are "similar" to the current trial [@Gastwirth2014, 289, 297]. Assessing such similarity implies weighting the available historical strike data with respect to some attorney-bias-related set of trial-level characteristics that are present or absent in the current trial.

>>>>

Simply pooling the the strike data from current and past trials, and analyzing such data together, ignores such incompatibility, which can lead to inflated type I error and reduced power [@Bennett2020]. To increase power, one may use other methods, such as stratifying strike data by trial and applying the Cochran-Mantel-Haenszel (CMH) test [@Gastwirth2014, 295-297]. Such approaches, however, do not directly address incompatibility between current and historical strike data. For example, applying the CMH test requires first selecting only historical strike data from past trials that are "similar" to the current trial [@Gastwirth2014, 289, 297]. Assessing such similarity implies selecting the available historical strike data with respect to some attorney-bias-related set of trial-level characteristics that are present or absent in the current trial with the goal of reducing the incompatibility between current and historical data.
